RDF Validation Requirements - Evaluation and Logical Underpinning

### 2015-01-06 paper/RDF validation requirements/RDF validation requirements.tex
replied to comments

\begin{itemize}
	\item R-56-INVERSE-OBJECT-PROPERTIES
\end{itemize}

\begin{itemize}
	\item In many cases properties are used bi-directionally and then accessed in the inverse direction, e.g. parent $\equiv$ child$^{-}$. There should be a way to declare value type, cardinality etc of those inverse relations without having to declare a new property URI. 
	\item The object property expression OPE1 is an inverse of the object property expression OPE2. Thus, if an individual x is connected by OPE1 to an individual y, then y is also connected by OPE2 to x, and vice versa.
\end{itemize}

@@

outdated:

\begin{gcotable}
property & $\top$ & parentOf & childOf$^{-}$ & - & $\equiv$ \\
\end{gcotable}

@@

alternative:

\begin{gcotable}
property & hasCaptain$^{-}$ & hasCaptain & - & - & inverse \\
property & captainOf & hasCaptain$^{-}$ & - & - & $\equiv$ \\
\end{gcotable}

alternative:

\begin{gcotable}
property & captainOf & hasCaptain & - & - & inverse \\
\end{gcotable}

@@

\begin{itemize}
	\item R-63-TRANSITIVE-OBJECT-PROPERTIES
\end{itemize}

\begin{itemize}
	\item Transitivity is a special form of complex role inclusion
	\item An object property transitivity axiom TransitiveObjectProperty( OPE ) states that the object property expression OPE is transitive — that is, if an individual x is connected by OPE to an individual y that is connected by OPE to an individual z, then x is also connected by OPE to z.
\end{itemize}

>>>>

\ms{Inverse Object Properties} corresponds to the requirement
\ms{R-56-INVERSE-} \ms{OBJECT-PROPERTIES}.
In many cases properties are used bi-directionally and then accessed in the inverse direction, e.g. parent $\equiv$ child$^{-}$. There should be a way to declare value type, cardinality etc of those inverse relations without having to declare a new property URI. 
The object property OP1 is an inverse of the object property OP2. 
Thus, if an individual x is connected by OP1 to an individual y, then y is also connected by OP2 to x, and vice versa.

@@

\begin{gcotable}
property & $\top$ & parentOf & childOf & - & inverse \\
\end{gcotable}

%outdated:
%
%\begin{gcotable}
%property & $\top$ & parentOf & childOf$^{-}$ & - & $\equiv$ \\
%\end{gcotable}

@@

%alternative:
%
%\begin{gcotable}
%property & hasCaptain$^{-}$ & hasCaptain & - & - & inverse \\
%property & captainOf & hasCaptain$^{-}$ & - & - & $\equiv$ \\
%\end{gcotable}
%
%alternative:
%
%\begin{gcotable}
%property & captainOf & hasCaptain & - & - & inverse \\
%\end{gcotable}

@@

\ms{Transitive Object Properties} corresponds to the requirement \\
\ms{R-63-TRANSITIVE-OBJECT-PROPERTIES}.
Transitivity is a special form of complex role inclusion.
An object property transitivity axiom states that the object property is transitive — that is, if an individual x is connected by the object property to an individual y that is connected by the object property to an individual z, then x is also connected by the object property to z.
